Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-06-26 2016-Weak-FH-Bisim/WeakBisim.tex
more indexes and explanations

We let $\gamma$ range over lists of action terms and use $\dotcup$ as the union that appends lists of action terms \TODO{write this properly}. $[a]$ is a list with a single element.

@@

\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} 

@@

 \TODO{Comment passer a ca?}\\

>>>>

We let $\gamma$ range over lists of action terms and use $\dotcup$ as the union that appends lists of action terms: given two  lists of action terms  $\gamma\dotcup\gamma '$ concatenates teh two lists. The operation is lifted to indexed sets of lists where  $\set {\gamma_1}\dotcup \set {\gamma_2}$ is an indexed set of lists that at each index concatenates the listof  list of $\set{\gamma_1}$ and the one of $\set {\gamma_2}$ (where one of the two lists is empty when $j\not \in \dom(\set{\gamma_1})$). $[a]$ is a list with a single element.

@@

\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}} \displaystyle{\bigvee_{b\in B}} 

@@

The three for all statements (on $J_a$, $J_b$, and $J_c$) can be concatenated using $\dotcup$, the list union lifted to indexed sets.\\
